
\begin{thebibliography}{7}

\bibitem{bougharriou}
{S. Bougharriou, F. Hamdaoui, and A. Mtibaa, "\textit{Linear SVM classifier based HOG car detection}", International Conference on Sciences and Techniques of Automatic Control and Computer Engineering (STA), 2017. }
	
\bibitem{prahara}
{Adhi Prahara and Murinto, "\textit{Car Detection Based on Road Direction on Traffic Surveillance Image}", International Conference on Science in Information Technology (ICSITech), 2016. }	

\bibitem{neumann}
{Daniel Neumann, Tobias Langner, Fritz Ulbrich, Dorothee Spitta1and Daniel Goehring, “\textit{Online  Vehicle  Detection  using  Haar-like,  LBP  and  HOG  Feature  basedImage  Classifiers  with  Stereo  Vision  Preselection}”, IEEE Intelligent Vehicles Symposium (IV), 2017.}

\bibitem{sajib}
{Md. Shamim Reza Sajib, and Dr. Saifuddin Md. Tareeq, “\textit{A Feature Based Method for Real Time Vehicle Detection and Classification From Om-Road Videos}”, International Conference of Computer an Informtion Technology (ICCIT), 2017.}
	
\bibitem{shakin}
{A. Shakin Banu and P. Vasuki, “\textit{Video Based Vehicle Detection using Morphological Operation and HOG Feature Extraction}”, ARPN Journal of Engineering and Applied Sciences, 2015.}

\bibitem{gonzalez}
{Gonzalez and Rafael C., “\textit{Digital Image Processing}”, Prentice-Hall, Inc., 2002.}

\bibitem{munir}
{Rinaldi Munir, “\textit{Pengolahan Citra Digital}”, Informatika, 2004.}

\bibitem{otsu}
{Otsu, N., “\textit{A  Threshold  Selection  Method  from Gray-Level  Histogram}”, Institute of Electrical and Electronics Engineers (IEEE), 1979}

\bibitem{dalal}
{Navneet Dalal and Bill Triggs, “\textit{Histograms of Oriented Gradients for Human Detection}”, Institute of Electrical and Electronics Engineers (IEEE), 2005}

\bibitem{opencv}
{"\textit{Histogram of Oriented Gradients}". [Online]. Available : https://www.learnopencv.com/histogram-of0oriented-gradients/.}

\bibitem{steinwart}
{Ingo Steinwart and Andreas Christmann , “\textit{Support Vector Machines}”, Information Science and Statistics. Springer, New York, 2008.}

\bibitem{confusion-matrix}
K. Markham, “Simple guide to confusion matrix terminology,” \textit{Data School}, 08-Jun-2016. [Online]. Available: https://www.dataschool.io/simple-guide-to-confusion-matrix-terminology/. [Accessed: 19-Sep-2018].

\bibitem{adhika}
{G. Adhika dan R.R.W. Ken, “\textit{Penerapan Histogram of Oriented Gradients, Principal Component Analysis, dan AdaBoost untuk Sistem Pengenalan Wajah}”, Institut Teknologi Harapan Bangsa (ITHB), 2018}

\end{thebibliography}

