
\begin{thebibliography}{19}
	
\bibitem{1}
{S. Karamizadeh, S. M. Abdullah, M. Halimi, J. Shayan and M. J. Rajabi. (2014). "\emph{Advantage and Drawback of Support Vector Machine Functionality}," IEEE 2014 International Conference on Computer, Communication, and Control Technology (I4CT 2014), September 2 - 4}

\bibitem{2}
{H. Zhang, "\emph{Exploring Conditions for the Optimality of Naive Bayes}," International Journal of Pattern Recognition and Artificial Intelligence, Vols. 19, No. 2, pp. 183-198.}

\bibitem{3}
{P. Domingos and M. Pazzani. (1997). "\emph{On the optimality of the simple Bayesian classifier under zero-one loss}," Machine learning, Vols. 29, No. 2-3, pp. 103-130}

\bibitem{4}
{A. R. and K. Alfalqi. (2015). "\emph{A Survey of Topic Modeling in Text Mining}," (IJACSA) International Journal of Advanced Computer Science and Applications, vol. 6 No. 1}

\bibitem{5}
{Y.-H. Chen and S.-F. Li. (2016). "\emph{Using Latent Dirichlet Allocation to Improve Text Classification Performance of Support Vector Machine}," Evolutionary Computation (CEC), 2016 IEEE Congress on}

\bibitem{6}
{N. Indurkhya and F. J. Damerau, \emph{Handbook of Natural Language Processing Second Edition}, Chapman \& Hall/CRC Machine Learning \& Pattern Recognition Series.}

\bibitem{7}
{F. Ricci, L. Rokach, B. Shapira and P. B. Kantor. (2011). \emph{Recommender Systems Handbook}, Springer New York Dordrecht Heidelberg London}

\bibitem{8}
{N. J. Nilsson. (2005). \emph{Introduction to Machine Learning}, Department of Computer Science Stanford University Stanford, CA 94305.}

\bibitem{9}
{A. K. Uysal and S. Gunal. (2014). "\emph{The Impact of Preprocessing on Text Classification}," Information Processing \& Management, vol. 50, no. 1, pp. 104-112}

\bibitem{10}
{W. M. Darling, "\emph{A Theoretical and Practical Implementation Tutorial on Topic Modeling and Gibbs Sampling}".}

\bibitem{11}
{Muhammad Ali Masood, Rabeeh Ayaz Abbasi, Onaiza Maqbool, Mubashar Mushtaq, Naif R. Aljohani, Ali Daud, Muhammad Ahtisham Aslam, Jalal S. Alowibdi. (2017). "\emph{MFS-LDA: a multi-feature space tag recommendation model for cold start problem}". Program, Vol. 51 Issue: 3, pp.218-234, https://doi.org/10.1108/PROG-01-2017-0002.}

\bibitem{12}
{Kurmashov, Nursultan, Konstantin Latuta, and Abay Nussipbekov. (2015). “\emph{Online Book Recommendation System}”. Twelve International Conference on Electronics Computer and Computation (ICECCO).}

\bibitem{13}
{David Alfred Ostrowski. (2015). “\emph{Using Latent Dirichlet Allocation for Topic Modelling in Twitter}”. Proceedings of the 2015 IEEE 9th International Conference on Semantic Computing (IEEE ICSC 2015).}

\bibitem{14}
{Anand Shanker Tewari, Tasif Sultan Ansari, and Asim Gopal Barman. (2014). “\emph{Opinion Based Book Recommendation Using Naive Bayes Classifier}”. Contemporary Computing and Informatics (IC3I), 2014 International Conference on.}

\bibitem{15}
{Keita Tsuji, Fuyuki Yoshikane, Sho Sato, and Hiroshi Itsumura. (2014). “\emph{Book Recommendation Using Machine Learning Methods Based on Library Loan Records and Bibliographic Information}”. 2014 IIAI 3rd International Conference on Advanced Applied Informatics.}

\bibitem{16}
{Khyati Pawde, Niharika Purbey, Shreya Gangan, Lakshmi Kurup. (2014). “\emph{Latent Semantic Analysis for Information Retrieval}”. International Journal of Engineering and Technical Research (IJETR) ISSN: 2321-0869, Volume-2, Issue-10.}

\bibitem{17}
{David M. Blei, Andrew Y. Ng, Michael I. Jordan. (2003). “\emph{Latent Dirichlet Allocation}”. Journal of Machine Learning Research 3 (2003) 993-1022.}

\bibitem{18}
{M. Allahyari, S. Pouriyeh, M. Assefi, S. Safaei, E. D. Trippe , J. B. Gutierrez and K. Kochut, "\emph{A Brief Survey of Text Mining Classification Clustering and Extraction Techniques}." 2017.}

\bibitem{19}
{Rafi, Muhammad, Shaikh, Mohammad Shahid. (2013). “\emph{An improved semantic similarity measure for document clustering based on topic maps}”, ICCET.}

\bibitem{20}
{Griffiths TL, Steyvers M (2004). “\emph{Finding Scientific Topics}.” Proceedings of the National Academy of Sciences of the United States of America, 101, 5228–5235.}

\end{thebibliography}
































